Jackknife

### 2021-02-23 analysis/rev_prototyping/jackknife.Rmd
fia

>>>>

fia <- load_dataset("fia_short")

fia_sites <- list_sites("fia_short")

fia_to_jk <- sample(fia_sites$site, size = 100, replace = F)

fia <- filter(fia, site %in% fia_to_jk)

fia_jacknives <-jacknife_whole_dataset(fia)

write.csv(fia_jacknives, here::here("analysis", "rev_prototyping", "jacknifed_datasets", "fia_jk.csv"), row.names = F)

fia_small <- load_dataset("fia_small")

fia_small_sites <- list_sites("fia_small")

fia_small_to_jk <- sample(fia_small_sites$site, size = 100, replace = F)

fia_small <- filter(fia_small, site %in% fia_small)

fia_small_jacknives <-jacknife_whole_dataset(fia_small)

write.csv(fia_small_jacknives, here::here("analysis", "rev_prototyping", "jacknifed_datasets", "fia_small_jk.csv"), row.names = F)
